Test functions on Alabama data

### 2016-09-29 Code/Test life expectancy fxs on Alabama.Rmd
playing with the plots

ggplot(alabama_age_decomp, aes(y = C_x, x = Ages)) + 
  geom_point() + 
  scale_y_continuous("Contribution of Age to Gap") +
  geom_abline(intercept = 0, slope = 0)

ggplot(alabama_age_decomp, aes(y = LE_Blacks, x = Ages)) + 
  geom_point(aes(col="Black")) + 
  scale_y_continuous("Life Expectancy (Yrs)") +
  geom_point(aes(y = LE_Whites, col="White")) +
  ggtitle("Life expectancy by age in black and white males in Alabama in 1969")
```

@@

ggplot(alabama_cod_decomp, aes(y = C_xi, x = COD2)) + 
  geom_point() + 
  scale_y_continuous("Contribution of Age to Gap") +
  geom_abline(intercept = 0, slope = 0) +
  facet_wrap(~Age2) + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

test <- plot_ly(data = alabama.by.strata, x = Year, y = Age3, z = log(mortality_rate,10),
        group = RaceSex, type = "heatmap", xaxis = paste0("x", id))

subplot(test)

ggplot(data = alabama.by.strata, aes(x=Year2, y = Age3)) + geom_tile(aes(fill = log(mortality_rate,10))) +
  facet_grid(Race2 ~ Sex2)

first.strata.cod2 <- alabama.by.strata.cod[alabama.by.strata.cod$RaceSex == "White.Male", ]
first.strata.cod2$Year3 <- as.numeric(as.character(first.strata.cod2$Year2))

@@

#this is wrong - need to create the dataset...
alabama.by.strata.cod2$id <- as.integer(alabama.by.strata.cod2$RaceSex)
subplot(plot_ly(data = subset(alabama.by.strata.cod2, COD2 == "Communicable"), x = Year3, y = Age3, z = cod_prop_death5, type = "heatmap", group = RaceSex, xaxis = paste0("x", id)))

first.strata.cod$id <- as.integer(first.strata.cod$COD2)
plot_ly(data = first.strata.cod, x = Year, y = Age3, z = log(cod_prop_death5, 10), type = "heatmap", group = COD2,
        xaxis = paste0("x", id))
```

>>>>

ggplot(alabama_age_decomp, aes(y = LE_Blacks, x = Ages)) + 
  geom_point(aes(col="Black")) + 
  scale_y_continuous("Life Expectancy (Yrs)") +
  geom_point(aes(y = LE_Whites, col="White")) +
  ggtitle("Life expectancy by age in black and white males in Alabama in 1969")

ggplot(alabama_age_decomp, aes(y = C_x, x = Ages)) + 
  geom_point() + 
  scale_y_continuous("Contribution of Age to Gap") +
  geom_abline(intercept = 0, slope = 0)
```

@@

ggplot(alabama_cod_decomp, aes(y = C_xi, x = COD2)) + 
  geom_point() + 
  scale_y_continuous("Contribution of cause of death to Gap") +
  geom_abline(intercept = 0, slope = 0) + facet_wrap(~ Age2) + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

#test <- plot_ly(data = alabama.by.strata, x = Year, y = Age3, z = log(mortality_rate,10),
#        group = RaceSex, xaxis = paste0("x", id), type = "heatmap")

#subplot(test)

#ggplot(data = alabama.by.strata, aes(x=Year3, y = Age3)) + geom_tile(aes(fill = log(mortality_rate,10))) +
#  facet_grid(Race2 ~ Sex2)

#first.strata.cod2 <- alabama.by.strata.cod[alabama.by.strata.cod$RaceSex == "White.Male", ]
first.strata.cod2 <- dat.clean.alabama[dat.clean.alabama$RaceSex == "White.Male", ]

@@

first.strata.cod2$id <- as.integer(first.strata.cod2$COD2)
plot_ly(data = first.strata.cod2, x = Year, y = Age3, z = cod_prop_death5, type = "heatmap", group = COD2,
        xaxis = paste0("x", id))

#this is wrong - need to create the dataset...
#alabama.by.strata.cod2$id <- as.integer(alabama.by.strata.cod2$RaceSex)
subplot(plot_ly(data = subset(alabama.by.strata.cod2, COD2 == "Communicable"), x = Year3, y = Age3, z = cod_prop_death5, type = "heatmap", group = RaceSex, xaxis = paste0("x", id)))

```
